Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-15 appendix.qmd
Updated Figure 1

## hexagon binning to have regular hexagons
hb_obj_scurve <- hex_binning(
  nldr_obj = scurve_scaled_obj, 
  bin1 = 8, 
  q = 0.1)

@@

## Generate all coordinates of hexagons
hex_grid <- hb_obj_scurve$hex_poly
```

```{r}
# Code to draw illustration for notation
start_pt <- all_centroids_df |> 
  filter(hexID == 1)
d_rect <- tibble(x1min = 0, 
                 x1max = 1,
                 x2min = 0,
                 x2max = diff(scurve_scaled_obj$nldr_obj$lim2)/diff(scurve_scaled_obj$nldr_obj$lim1))

@@

a1 <- tibble(x = all_centroids_df$c_x[4],
             xend = all_centroids_df$c_x[5],
             y = all_centroids_df$c_y[21],
             yend = all_centroids_df$c_y[21],
             label = expression(a[1]))
a2 <- tibble(x = all_centroids_df$c_x[27],
             xend = all_centroids_df$c_x[27],
             y = all_centroids_df$c_y[27],
             yend = all_centroids_df$c_y[33],
             label = expression(a[2]))

@@

@@

>>>>

@@

a1_temp <- hb_obj_scurve$a1
a2_temp <- hb_obj_scurve$a2
l_temp <- quad(a=3, b = 2 * a2_temp, c = -(a2_temp^2 + a1_temp^2))

```{r}
# Code to draw illustration for notation
start_pt <- all_centroids_df |> 
  filter(hexID == 1)

d_rect <- tibble(x1min = 0, 
                 x1max = 1,
                 x2min = 0,
                 x2max = diff(scurve_scaled_obj$lim2)/diff(scurve_scaled_obj$lim1))

hex_grid_temp40 <- hex_grid |> 
  filter(hex_poly_id == 53)

@@

a1 <- tibble(x = all_centroids_df$c_x[4],
             xend = all_centroids_df$c_x[5],
             y = all_centroids_df$c_y[29],
             yend = all_centroids_df$c_y[29],
             label = expression(a[1]))
a2 <- tibble(x = all_centroids_df$c_x[39],
             xend = all_centroids_df$c_x[39],
             y = all_centroids_df$c_y[39],
             yend = all_centroids_df$c_y[47],
             label = expression(a[2]))

l <- tibble(x = hex_grid_temp40$x[2],
            xend = hex_grid_temp40$x[3],
            y = hex_grid_temp40$y[2],
            yend = hex_grid_temp40$y[3],
            label = expression(l))

@@

      color = "black", size = 8) +
  geom_segment(data = l, aes(

@@

    annotate("text", x=l$x + 0.03, y=(l$y+l$yend)/2, 
             label = expression(l), 
             color = "black", hjust=-0.2, size = 8) +
